---
title: "World Happiness Report 2021"
author: "from Kaggle.com"
date: '2020-12-01T21:13:14-05:00'
categories: R
tags:
- R Markdown
- produce
- progression
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
library(tidyverse)

#importing datatables
world_happy <- read.csv("data/world-happiness-report.csv")
world_happy2021 <- read.csv("data/world-happiness-report-2021.csv")
```

Some world statistics about countries according to various measures:

(Database downloaded from **kaggle.com.**)

## Top 10 Countries According to Logged GDP Per Capita in 2020

``` {r echo=FALSE}
world_happy2020 <-
  world_happy %>%
  dplyr::filter(year == "2020")
  
world_happy2020 %>%
  select(ď.żCountry.name,Log.GDP.per.capita) %>%
  arrange(desc(Log.GDP.per.capita)) %>%
  slice_head(n = 10)  


```

## Top 10 Countries According to Social Support in 2021

``` {r echo=FALSE}
world_happy2021 %>%
  select(ď.żCountry.name,Social.support) %>%
  arrange(desc(Social.support)) %>%
  slice_head(n = 10) 

```

## Number of countries with life expectancy equal or higher than 70 between 2005 and 2020

```{r echo=FALSE}
world_happy %>%
  filter(Healthy.life.expectancy.at.birth >= 70)  %>%
  group_by(year) %>%
  summarise(
    No_of_Countries = n(),
  )


```

## Top 5 Countries according to Happiness Index ("Life Ladder") in 2021

```{r message=FALSE, warning=FALSE, echo=FALSE}


world_happy2021 %>%
  select(ď.żCountry.name,Ladder.score) %>%
  #group_by(ď.żCountry.name) %>%
  arrange(desc(world_happy2021$Ladder.score)) %>%
  slice_head(n = 5)  %>%
  ggplot() + 
  aes(
    x = fct_inorder(ď.żCountry.name, Ladder.score),
    y = Ladder.score,
    fill = Ladder.score) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(
    x = "Country",
    y = "Ladder Score",
    title = 'The 5 Happiest Countries in 2021 ("Happiness Index")'
    ) +
  geom_text (
    aes(label = Ladder.score),
    size = 5,
    hjust = 0.5,
    vjust = 3,
    position = "stack",
    color = "black") +
  scale_fill_gradient (
    low = "beige",
    high = "gold"
    ) +
  scale_y_continuous(
    expand = c(0,0),
    limits = c(0,8)) +
  theme_minimal() +
  theme(
    axis.line = element_line(size = 0.7, color = "gold"),
    legend.position = "none"
    )

```

Below you may find some statistical descriptions of used tables.

### Database statistics summary about World Happiness Table:

```{r echo=FALSE}
skimr::skim(world_happy)
```

### Database statistics summary about World Happiness 2021 Table:

```{r echo=FALSE}
skimr::skim(world_happy2021)
```